\cleardoublepage
\addcontentsline{toc}{chapter}{Bibliography}

\begin{thebibliography}{99}

\bibitem{FirstRover}
NASA, ``Luna 17 / Lunokhod 1,'' NASA Solar System Exploration. [Online]. Available: \url{https://solarsystem.nasa.gov/missions/lunokhod-01/in-depth/}. Accessed: May 2026.

\bibitem{nasa_mars_rovers}
NASA, ``Mars Rovers,'' NASA Mars Exploration Program, 2022. [Online]. Available: \url{https://mars.nasa.gov/mars-exploration/missions/}. Accessed: May 2026.

\bibitem{perseverance_cost}
The Planetary Society, ``Cost of Perseverance,'' 2020. [Online]. Available: \url{https://www.planetary.org/space-policy/cost-of-perseverance}. Accessed: May 2026.

\bibitem{look}
Norwegian Space Cluster, ``LOOK: Lunar rObOt Konkurranse,'' 2026. [Online]. Available: \url{https://www.norwegianspacecluster.no/look}. Accessed: May 2026.

\bibitem{Lunokhod}
D. A. Kring, ``Lunar Mobility Review,'' Lunar and Planetary Institute, 2006. [Online]. Available: \url{https://www.lpi.usra.edu/science/kring/lunar_exploration/briefings/lunar_mobility_review.pdf}. Accessed: May 2026.

\bibitem{Mars2020Wheels}
A. Greicius, ``Mars 2020 stands on its own six wheels,'' NASA, Oct. 24, 2019. [Online]. Available: \url{https://www.nasa.gov/solar-system/mars-2020-stands-on-its-own-six-wheels/}. Accessed: May 2026.

\bibitem{SpaceLatency}
D. Lester and H. Thronson, ``Human space exploration and human space flight: Latency and the cognitive scale of the universe,'' NASA Technical Reports Server, 2011. [Online]. Available: \url{https://ntrs.nasa.gov/api/citations/20110024057/downloads/20110024057.pdf}. Accessed: May 2026.

\bibitem{VIPER}
NASA Science, ``VIPER,'' NASA. [Online]. Available: \url{https://science.nasa.gov/mission/viper/}. Accessed: May 2026.

\bibitem{PerseveranceAutoNav}
Jet Propulsion Laboratory, ``NASA's self-driving Perseverance Mars rover takes the wheel,'' NASA/JPL, Jul. 1, 2021. [Online]. Available: \url{https://www.jpl.nasa.gov/news/nasas-self-driving-perseverance-mars-rover-takes-the-wheel/}. Accessed: May 2026.

\bibitem{LowCostLiDAR}
E. Ferreira \textit{et al.}, ``Development of a low-cost 3D mapping technology with 2D LIDAR for path planning based on the A-Star algorithm,'' in \textit{Robot 2023: Sixth Iberian Robotics Conference}, L. Marques, C. Santos, J. L. Lima, D. Tardioli, and M. Ferre, Eds. Cham, Switzerland: Springer, 2024, pp. 53--66, doi: 10.1007/978-3-031-58676-7\_5. [Online]. Available: \url{https://link.springer.com/chapter/10.1007/978-3-031-58676-7_5}. Accessed: May 2026.

\bibitem{RPLIDARDatasheet}
SLAMTEC, ``RPLIDAR C1 Datasheet v1.0,'' Shanghai Slamtec Co., Ltd., 2023. [Online]. Available: \url{https://static.generation-robots.com/media/slamtec-rplidar-c1-datasheet.pdf}. Accessed: May 2026.

\bibitem{ToFOverview}
R. Horaud, M. Hansard, G. Evangelidis, and C. Menier, ``An overview of depth cameras and range scanners based on time-of-flight technologies,'' \textit{Machine Vision and Applications}, vol. 27, pp. 1005--1020, 2016. [Online]. Available: \url{https://arxiv.org/abs/2012.06772}. Accessed: May 2026.

\bibitem{StepperBasics}
Oriental Motor, ``Stepper motor basics,'' Oriental Motor. [Online]. Available: \url{https://www.orientalmotor.com/stepper-motors/technology/stepper-motor-basics.html}. Accessed: May 2026.

\bibitem{NEMA17Datasheet}
PBC Linear, ``Stepper Motor NEMA 17,'' data sheet. [Online]. Available: \url{https://media.pbclinear.com/pdfs/pbc-linear-data-sheets/data-sheet-stepper-motor-support.pdf}. Accessed: May 2026.

\bibitem{MicrosteppingTI}
D. Mitra, ``How to improve motion smoothness and accuracy of stepper motors,'' Texas Instruments, Application Report SLOA293A, 2021. [Online]. Available: \url{https://www.ti.com/lit/an/sloa293a/sloa293a.pdf}. Accessed: May 2026.

\bibitem{Makerbase}
Makerbase, ``SERVO42D NEMA17 Closed Loop Stepper Motor.'' [Online]. Available: \url{https://makerbase3d.com/product/servo42d-nema17-closed-loop-stepper-motor-driver-cnc-3d-printer-for-gen_l-foc-quiet-and-efficient/}. Accessed: May 2026.

\bibitem{PIDUMich}
University of Michigan, ``Introduction: PID controller design,'' Control Tutorials for MATLAB and Simulink. [Online]. Available: \url{https://ctms.engin.umich.edu/CTMS/index.php?example=Introduction&section=ControlPID}. Accessed: May 2026.

\bibitem{RS485DesignGuide}
Texas Instruments, ``The RS-485 Design Guide,'' Application Report SLLA272D, 2024. [Online]. Available: \url{https://www.ti.com/lit/pdf/slla272}. Accessed: May 2026.

\bibitem{ModbusSerialLine}
Modbus Organization, ``MODBUS over Serial Line Specification and Implementation Guide V1.02,'' Dec. 20, 2006. [Online]. Available: \url{https://www.modbus.org/file/secure/modbusoverserial.pdf}. Accessed: May 2026.

\bibitem{ModbusApplicationProtocol}
Modbus Organization, ``MODBUS Application Protocol Specification V1.1b3,'' Apr. 26, 2012. [Online]. Available: \url{https://www.modbus.org/file/secure/modbusprotocolspecification.pdf}. Accessed: May 2026.

\bibitem{rpi_power}
Raspberry Pi Foundation, ``Raspberry Pi 5 Power Consumption,'' Raspberry Pi Documentation, 2023. [Online]. Available: \url{https://www.raspberrypi.com/documentation/computers/raspberry-pi.html#power-consumption}. Accessed: May 2026.

\bibitem{IMUDatasheet}
SparkFun Electronics, ``SparkFun 9DoF IMU ICM-20948 Breakout Hookup Guide.'' [Online]. Available: \url{https://learn.sparkfun.com/tutorials/sparkfun-9dof-imu-icm-20948-breakout-hookup-guide/all}. Accessed: May 2026.

\bibitem{INA226Datasheet}
Texas Instruments, ``INA226 High-Side or Low-Side Measurement, Bidirectional Current and Power Monitor,'' data sheet. [Online]. Available: \url{https://www.ti.com/lit/ds/symlink/ina226.pdf}. Accessed: May 2026.

\bibitem{battery_datasheet}
RS PRO, ``14.8V Lithium-Ion Rechargeable Battery Pack, 5.2Ah,'' data sheet. [Online]. Available: \url{https://docs.rs-online.com/7c4d/A700000008880235.pdf}. Accessed: May 2026.

\bibitem{BambuLabASA}
Bambu Lab, ``Bambu Filament Technical Data Sheet V3.0: ASA,'' Bambu Lab. [Online]. Available: \url{https://wiki.bambulab.com/filament-acc/abs-asa-pc/6eaf4c432d1d4014a1975e55a55ed00b.pdf}. Accessed: May 2026.

\bibitem{MatWebASA}
MatWeb, ``ASA material property data,'' MatWeb. [Online]. Available: \url{https://www.matweb.com/search/datasheet.aspx?matguid=24c5655bc30e42c3949df6c53122bd61}. Accessed: May 2026.

\bibitem{NASA_STD5001B}
NASA, ``NASA-STD-5001B: Structural design and test factors of safety,'' 2022. [Online]. Available: \url{https://standards.nasa.gov/standard/NASA/NASA-STD-5001}. Accessed: May 2026.

\bibitem{Zou2016}
R. Zou \textit{et al.}, ``Isotropic and anisotropic elasticity of 3D printed material,'' \textit{Composites Part B: Engineering}, vol. 99, pp. 506--513, 2016, doi: 10.1016/j.compositesb.2016.06.009.

\bibitem{Wilcox2020}
R. B. Wilcox, \textit{Basic Applied Finite Element Analysis}, PDHonline Course G180, PDH Center, 2020. [Online]. Available: \url{https://www.pdhonline.com/courses/g180/g180content.pdf}. Accessed: May 2026.

\bibitem{hibbeler_2018}
R. C. Hibbeler, \textit{Mechanics of Materials in SI Units}, 10th ed. Harlow, U.K.: Pearson Education Limited, 2018.

\bibitem{jong_von_mises_2009}
I.-C. Jong and W. T. Springer, ``Teaching von Mises Stress: From Principal Axes to Nonprincipal Axes,'' in \textit{Proc. 2009 ASEE Annual Conference \& Exposition}, Austin, TX, USA, Jun. 2009, pp. 14.1159.1--14.1159.9, doi: 10.18260/1-2--5353.

\bibitem{solidworks_von_mises_2025}
Dassault Syst\`emes SOLIDWORKS, ``Maximum von Mises Stress Criterion,'' \textit{SOLIDWORKS Web Help}, 2025. [Online]. Available: \url{https://help.solidworks.com/2025/english/SolidWorks/cworks/r_Maximum_von_Mises_Stress_Criterion.htm}. Accessed: May 2026.

\bibitem{wevolver_asa_vs_pla}
Wevolver, ``ASA vs PLA: Comparing 3D printing filaments,'' Wevolver. [Online]. Available: \url{https://www.wevolver.com/article/asa-vs-pla}. Accessed: May 2026.
\end{thebibliography}